\documentclass[10pt, letterpaper]{article}

\usepackage[singlespacing]{setspace}
\usepackage[letterpaper,margin=0.75in]{geometry}

\usepackage{graphicx}                               
\usepackage{amssymb}                                    
\usepackage{amsmath}                                    
\usepackage{amsthm}                                          

\usepackage{alltt}                                      
\usepackage{float}
\usepackage{color}
\usepackage{url}

\usepackage{balance}
\usepackage[TABBOTCAP, tight]{subfigure}
\usepackage{enumitem}
\usepackage{pstricks, pst-node}

%random comment

\newcommand{\cred}[1]{{\color{red}#1}}
\newcommand{\cblue}[1]{{\color{blue}#1}}

\newcommand{\toc}{\tableofcontents}

\usepackage{hyperref}
\usepackage{geometry}
\usepackage{longtable}
\usepackage[utf8]{inputenc}

\def\name{Yeongae Lee, Johonny Chunyi Po, Andrew Davis}

%% The following metadata will show up in the PDF properties
\hypersetup{
  colorlinks = true,
  urlcolor = black,
  pdfauthor = {\name},
  pdfkeywords = {cs444 ``operating systemsII''},
  pdftitle = {CS 444 HW 1},
  pdfsubject = {CS 444 Project 1},
  pdfpagemode = UseNone
}

\begin{document}

\begin{titlepage}

    \begin{center}
        \vspace*{5cm}
        
        \textbf{CS 444 Project 1}

        \vspace{1.5cm}

        \textbf{Yeongae Lee, Johonny Chunyi Po, Andrew Davis}

        \vspace{0.8cm}

        Oregon State University\\
        CS 444\\
        Spring 2018\\
        15 April 2018\\

        \vspace{0.8cm}

        \textbf{Abstract}\\

        \vspace{0.5cm}

        Here

        \vfill
    \end{center}
\end{titlepage}

\newpage


\section{Commands}

    \begin{enumerate}
        \item git clone https://git.yoctoproject.org/git/linux-yocto
        \item cd linux-yocto
        \item git checkout v3.19.2
        \item cd /scratch/spring2018/
        \item mkdir group39
        \item git clone https://git.yoctoproject.org/git/linux-yocto
        \item cd linux-yocto
        \item git checkout v3.19.2
        \item cd /scratch/opt/
        \item cp config-3.19.2-yocto-standard 
        \item mv config-3.19.2-yocto-standard .config 
        \item make -j4 all
        \item make clean
        \item make menuconfig
        \item make -j4 all
        \item cd /scratch/files/ 
        \item qemu-system-i386 -gdb tcp::5539 -S -nographic -kernel bzImage-qemux86.bin -drive file=core-image-lsb-sdk-qemux86.ext4,if=virtio -enable-kvm -net none -usb -localtime --no-reboot --append "root=/dev/vda rw console=ttyS0 debug"
        \item cp core-image-lsb-sdk-qemux86.ext4 /scratch/spring2018/gourp39/linux-yocto
        \item cp bzImage-qemux86.bin /scratch/spring2018/gourp39/linux-yocto
        \item qemu-system-i386 -gdb tcp::5539 -S -nographic -kernel bzImage-qemux86.bin -drive file=core-image-lsb-sdk-qemux86.ext4,if=virtio -enable-kvm -net none -usb -localtime --no-reboot --append "root=/dev/vda rw console=ttyS0 debug"
        \item gdi
        \item target remote localhost:5539
        \item
        \item
        \item
        \item
        \item
        \item
        \item
        \item
        \item
        \item
    \end{enumerate}
    
    
\section{Questions}

    \begin{enumerate}
        \item What do you think the main point of this assignment is? \\
            Anwser should be here
            
        \item How did you personally approach the problem? Design decisions, algorithm, etc. \\
            Anwser should be here
            
        \item How did you ensure your solution was correct? Testing details, for instance. \\
            Anwser should be here
            
        \item What did you learn? \\
            Anwser should be here
            
    \end{enumerate}
 

\section{Version control log}

    \begin{tabular}{l l l }
        \hline
         Date & Author & Description \\
        \hline
         4/12/2018 & Johnny & Initial Commit  \\
         4/12/2018 & Johnny & First commit and push to repo \\
         4/12/2018 & Johnny & Merge branch 'master' of https://github.com/jawhnypoh/Operating-Systems-II \\
         4/12/2018 & Johnny & Deleted acl_open - unnecessary file \\
         4/13/2018 & Yeongae & Made Assignment1 directory \\
         4/13/2018 & Yeongae & Changed main.tex \\
         
         %more commits should be here 
         
         
        \hline
    \end{tabular}


\section{Work log}

    \begin{tabular}{l l l l }
        \hline
         Date & Title & Author & Description \\
        \hline
         4/7/2018 & VM and qemu & Johonny & Built kernel and run qemu \\
         4/9/2018 & VM and qemu & Andrew & Built kernel and run qemu \\
         4/9/2018 & VM and qemu & Yeongae & Built kernel and run qemu \\
         4/12/2018 & Version control & Johonny & Opened git repository \\
         4/13/2018 & LaTeX & Yeongae & Wrote LaTeX file outline\\
         4/13/2018 & Write-up & Johnny & Wrote LaTeX file \\
         4/13/2018 & Write-up & Yeongae & Wrote LaTeX file \\
        \hline
    \end{tabular}
    

\begin{thebibliography}{9}
 
    \bibitem{knuthwebsite} 
    D. Kevin McGrath: makefile,
    \\\texttt{http://web.engr.oregonstate.edu/cgi-bin/cgiwrap/dmcgrath/classes/17F/cs444/index.cgi?
    \\examples=examples/makefile}
  
    \bibitem{knuthwebsite} 
    D. Kevin McGrath: example.tex,
    \\\texttt{http://web.engr.oregonstate.edu/cgi-bin/cgiwrap/dmcgrath/classes/17F/cs444/index.cgi?
    \\examples=examples/example.tex}

\end{thebibliography}


\end{document}
